Escape Analysis and Specialization in a Tracing JIT

### 2010-09-28 talk/pepm2011/paper.tex
add some references

Tracing JITs are a recently popular approach to write just-in-time
compilers for dynamic languages \cite{XXX}. Their origins lie in the Dynamo
project, which used a tracing approach to optimize machine code using execution
traces \cite{XXX}. Tracing JITs have then be adapted to be used for a very light-weight
Java VM \cite{XXX} and afterwards used in several implementations of dynamic
languages, such as JavaScript \cite{XXX}, Lua \cite{XXX} and now Python via
PyPy.

>>>>

Tracing JITs are a recently popular approach to write just-in-time compilers for
dynamic languages. Their origins lie in the Dynamo project, which used a tracing
approach to optimize machine code using execution traces
\cite{bala_dynamo:_2000}. Tracing JITs have then be adapted to be used for a
very light-weight Java VM \cite{gal_hotpathvm:_2006} and afterwards used in
several implementations of dynamic languages, such as JavaScript
\cite{andreas_gal_trace-based_2009}, Lua \cite{XXX} and now Python (and other
languages) via PyPy.
